Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-07-11 Journal1/Response3/Response.tex

%\usepackage{fixltx2e}
\usepackage{amsmath, amssymb, upgreek, amsthm}
\usepackage{graphicx}
\usepackage{tikz}
\geometry{letterpaper, left=20mm, right=20mm, top=20mm, bottom=20mm}
\usetikzlibrary{patterns} % LATEX and plain TEX when using Tik Z
\allowdisplaybreaks
\setlength{\textfloatsep}{2ex}
\usepackage{array}
\usepackage{enumitem}
\setlength{\parindent}{1 em}
\setlength{\parskip}{0.5 em}
\renewcommand{\baselinestretch}{1.25}
\def\dsd{d_\text{SD}}
\def\Rcoop{R_\text{Coop}}
\def\rhd{R_\text{HD}}
\def\rsd{R_\text{SD}}
\def\rsh{R_\text{SH}}
\def\Pcoops{\mathcal{P}^\text{Succ}_\text{Coop}}
\def\dsh{d_\text{SH}}
\def\dhd{d_\text{HD}}
\def\psibar{\overline{\mathcal{P}}^\text{Succ}_{i}}
\def\psbara{\overline{\mathcal{P}}^\text{Succ}_{1}}
\def\psbarb{\overline{\mathcal{P}}^\text{Succ}_{2}}
\def\psbarc{\overline{\mathcal{P}}^\text{Succ}_{3}}
\def\psbard{\overline{\mathcal{P}}^\text{Succ}_{4}}
\def\psbare{\overline{\mathcal{P}}^\text{Succ}_{5}}
\def\Ri{R_{i}}
\def\Ps{\mathcal{P}^\text{Succ}_\text{Direct}}
\def\frk{\mathrm{f}_{r_k}(r)}
\def\Rcoopj{R_\text{coop}^j}
\title{\bf \vspace*{-4ex} Statement of Responses to the Editor and the Reviewers of Paper-TNSM \\[-6ex]}
\date{}

\begin{document}
%\vspace*{-10ex}
%\sloppy
\maketitle
We would like to thank the editor and reviewers for their constructive comments on our manuscript. They have been beneficial in revising this paper, and we have improved both the technical content and presentation quality through their assistance. We greatly appreciate their generous help. Moreover, we have reviewed and incorporated all the comments and suggestions.
We hope that the modifications we have made to the manuscript and the responses we have provided herein will alleviate the reviewers' concerns. Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
\\ [-3.ex]
% % % % % % % % % % % % % % % Editor % % % % % % % % % % % % % % % % % % % %

@@

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Editor} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent  Comments to the Author} ``I think the paper should undergo a major revision. It is important to take special attention to the comments of reviewer 2.''\\
\hline
\end{longtable}

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the Editor for his comments and for giving us this opportunity to improve our paper. We have used the comments to improve our paper and eliminate problems.

@@

%\begin{longtable}{|p{0.975\textwidth}|}
%\hline \hline
%\RaggedRight
%\cellcolor{green!10}
%[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.
%\\
%\hline
%\end{longtable}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The authors have addressed the comments provided in a previous review. The contributions are clear and the results are compared to some related work, so the reader can somewhat contextualize the proposed solution. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can alleviate the reviewer's concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``However, the paper still needs some improvement in terms of readability. Some paragraphs are too long  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We revised the whole paper and checked the text entirely according to this comment. For instance, the introduction has been rewritten totally. We also revised the system model, proposed algorithms too, and shortened long paragraphs based on these comments. Moreover, we shortened the numerical results and feasible region section, and modified the conslusion section.  
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} `` the figures are difficult to locate from their reference in the text (figures at top, as typical IEEE template is better), the text in the figures is too small ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Thank you for this comment. We think that these changes improve the readability of the manuscripts.
 We modified all the paper's figures entirely concerning this comment and located them in sub-figures to make them more determined. Moreover, we modified whole the figures and made the texts larger and more readable. 
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} ``the contributions discussed in the introduction are not easily found in the other parts of the paper.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We thank the reviewer for asking us to add clarity to our paper and reducing ambiguity in this condition.  We changed the contribution in a better way based on this comment. We have removed some sentences and rewritten the contributions in the same order of our paper's section.
Below we report the whole contribution section.

@@

  UE &  user equipment \\ [.5ex]
  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
  CAPEX & capital expenditures  \\ [.5ex]
  OPEX & operating expenses  \\ [.5ex]

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \end{table}

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment11:} `Finally, the figures in the current version of the manuscript are very small and extremely hard to read. Therefore, re-formatting is necessary. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We modified all figures to make it more readable.

\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 3} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The reviewer has addressed most of the comments satisfactorily. However, the paper still contains some minor issues as follows ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We are pleased to thank the reviewer for his/her detailed and thorough reading of this manuscript. We hope that the responses provided here will assist the reviewer in relieving his or her concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``Abbreviations such as QoS, CAPEX and OPEX are not expanded at their first use. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Based on this comment, we added a Table I reporting the list of acronyms to the paper that is shown as below

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \end{table}
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} ``Eq. (3) includes inter-slice interference but a sentence following the equation mentions that there is no inter-slice interference because slices are isolated, which is confusing''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\} 
We thank the reviewer for reporting this ambiguity.
We revised this section, rewrote the equation (3), by removing the inter-slice interference to clarify this equation. Moreover, we removed two figures of Fig. 2 and Fig. 3 since they don't add much to what is already written in words, and even Fig. 2 makes the paper vaguer, and we also aim for a more concise manuscript.
Below we report the revised sentences.

Network slicing techniques significantly reduce inter-service (inter-slice) interference.
One way consists in leveraging a two-time scale PRB scheduling to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale). Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC [2], [5], [32]. In this paper, we assume that the PRB scheduling is performed. Also, in Section V-A, we briefly study the PRB scheduling between slices.
Since there are limited resources, inter-service interference cannot be eliminated entirely. Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.
Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as 
%{\color{red} use paranthesis in the following equation to clear +}
%\begin{subequations}\label{eqI}
%\begin{alignat}{4}
%\begin{align}\label{eqI}
%&I_{r,u(s,i)}^{k} =\nonumber\\
% &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
%&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
%&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
%\end{align}
%\end{alignat}
%\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
\begin{align}\label{eqI}
&I_{r,u(s,i)}^{k} =+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}}\nonumber\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
\end{align}
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is a binary variable that indicates whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU, or not. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
Furthermore, there is no inter-slice interference, only intra-slice interference, since slices are assumed to be isolated. 
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} ``The captions of Figs. 9, 12 and 14 are incomplete.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}  
Thank you for this comment. We checked and corrected all the figure's captions.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment4:} ``It is recommended to discuss each result figure in one paragraph. Currently, the discussions on Figs. 5-11 are packed into one paragraph, which is difficult to read.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}  
We would like to thank the reviewer for reducing the ambiguity of our paper with this comment. Each figure was discussed as an individual paragraph in response to this comment.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment5:} ``Another round of proofread is required, as there are some mathematical variables which are not italicized and some sentences are incomplete.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}  
We modified the whole paper based on this comment, tried correcting all mathematical variables, and revised all sentences again. We checked all the system model and proposed algorithms and corrected the italicized text and vice versa. For instance, we corrected the $\log$, $\max$, and $\min$ and other texts that are written in italics. Moreover, we italicized variables that were written in non-italicized.
\end{document}

### 2022-07-11 Journal1/paper5TNSM - Copy/pr.tex
add revised

Network slicing techniques significantly reduce inter-service interference.
One way consists in leveraging a two-time scale PRB scheduling to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale). Since there are limited resources, inter-service interference cannot be eliminated entirely. Another method consists of allocating part of the PRBs of eMBB services to URLLC, and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}. In this paper, we assume that the PRB scheduling is performed. Also, in Section \ref{prb}, we briefly study the PRB scheduling between slices.
%\begin{figure}
%  \centering
%  \captionsetup{justification=centering}
%    \includegraphics[scale = 0.35]{Interference.png}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Type of Interference Signal}
%  \label{fig:intf}
%\end{figure}

Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization, and can be represented as 
%{\color{red} use paranthesis in the following equation to clear +}
%\begin{subequations}\label{eqI}
%\begin{alignat}{4}
\begin{align}\label{eqI}
&I_{r,u(s,i)}^{k} =\nonumber\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{align}
%\end{alignat}
%\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is a binary variable that indicates whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU, or not. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
Furthermore, there is no inter-slice interference, only intra-slice interference, slices are assumed to be isolated.

@@

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of the O-RU and the Fronthaul Capacity}
Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to all the UEs served by it. From \eqref{eq2}, the power of each O-RU $r$ is obtained as follows,
%{\color{red} is this the sum rate of all users?}
\begin{equation}\label{pr}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2\alpha^k_{r,u(s,i)} + \sigma_{q}^2,
\end{equation}
where $\alpha^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$.
Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{align}\label{cr}
C_{r} &= \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},\nonumber\\
C_{r} &= \log_2{\left(\frac{P_r}{ \sigma_{q}^2}\right)}.
\end{align}
\subsection{Mean Delay}
In this part, the end-to-end mean delay for each service is obtained.
The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the total propagation delay ($T^{\text{pro}}$).
\begin{subequations}
\begin{alignat}{4}
T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
T^{\text{\text{proc}}} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}.
\end{alignat}
\end{subequations}
%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Mathematically, the total propagation delay ($T^{\text{pro}}$) is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$. In each link, the propagation delay is the time a signal to reach its destination. It is obtained based on the length of the fiber link and the capacity of the link (as $\text{T} = \text{L}/\text{c}$, where L is the length of the link and c is the propagation speed of the medium).
Meanwhile, the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
In each link, the transmission delay is the amount of time required to push all the packets into the transmission medium, and can formulated as
$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the data-rate of the packet and $\mathcal{\alpha}$ is the mean packet size.
Notice that taking the propagation and transmission delays into account in the formulation is straightforward, but we have avoided it for the sake of succinctness and simplicity.

@@

\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r,

@@

&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i, r, s, k,\label{c12-1} \\
&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{min} \quad \forall s, \label{c13} \\

@@

& C_r \leq C^{max}_r \quad \forall r, \label{c15}\\
&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i, s,\label{c16} \\

@@

& 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\
& \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\

@@

Suppose, $\mathcal{R}_{{s}}^{min}$, and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.

@@

Therefore, the minimum number of PRBs that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$. 
Moreover, the maximum number of PRB that the slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$. Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRBs in slice s.

@@

& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\

@@

\subsection{Sub-Problem 1}\label{sub1}
Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
Here, we first simplify and relax the parameters to convexify the problem.
As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
for $\rho_{u(s,i)}^{k}$.
Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.

>>>>

\textcolor{MidnightBlue}{Network slicing techniques significantly reduce inter-service (inter-slice) interference.
One way consists in leveraging a two-time scale PRB scheduling to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale). Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}. In this paper, we assume that the PRB scheduling is performed. Also, in Section \ref{prb}, we briefly study the PRB scheduling between slices.
Since there are limited resources, inter-service interference cannot be eliminated entirely. Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.}
%\begin{figure}
%  \centering
%  \captionsetup{justification=centering}
%    \includegraphics[scale = 0.35]{Interference.png}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Type of Interference Signal}
%  \label{fig:intf}
%\end{figure}

\textcolor{MidnightBlue}{Back to \eqref{eq1}, $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as }
%{\color{red} use paranthesis in the following equation to clear +}
%\begin{subequations}\label{eqI}
%\begin{alignat}{4}
%\begin{align}\label{eqI}
%&I_{r,u(s,i)}^{k} =\nonumber\\
% &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
%&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
%&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
%\end{align}
%\end{alignat}
%\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
\begin{align}\label{eqI}
&I_{r,u(s,i)}^{k} =+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}}\nonumber\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
\end{align}
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is a binary variable that indicates whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU, or not. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
Furthermore, there is no inter-slice interference, only intra-slice interference, since slices are assumed to be isolated.

@@

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{\text{max}}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of the O-RU and the Fronthaul Capacity}
Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to all the UEs served by it. From \eqref{eq2}, the power of each O-RU $r$ is obtained as follows,
%{\color{red} is this the sum rate of all users?}
\begin{equation}\label{pr}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2\alpha^k_{r,u(s,i)} + \sigma_{q}^2,
\end{equation}
where $\alpha^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$.
Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{align}\label{cr}
C_{r} &= \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},\nonumber\\
C_{r} &= \log_2{\left(\frac{P_r}{ \sigma_{q}^2}\right)}.
\end{align}
\subsection{Mean Delay}
In this part, the end-to-end mean delay for each service is obtained.
The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the total propagation delay ($T^{\text{pro}}$).
\begin{subequations}
\begin{alignat}{4}
T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
T^{\text{\text{proc}}} &=  T^{\text{RU}} + T^{\text{DU}} + T^{\text{CU}} + T^{\text{UPF}},\\
T^{\text{tr}} &= T^{\text{fr},t} + T^{\text{mid},t} + T^{\text{b},t},  \\
T^{\text{pro}} &= T^{\text{fr},p} + T^{\text{mid},p} + T^{b,p}.
\end{alignat}
\end{subequations}
%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Mathematically, the total propagation delay ($T^{\text{pro}}$) is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$. In each link, the propagation delay is the time a signal to reach its destination. It is obtained based on the length of the fiber link and the capacity of the link (as $\text{T} = \text{L}/\text{c}$, where L is the length of the link and c is the propagation speed of the medium).
Meanwhile, the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
In each link, the transmission delay is the amount of time required to push all the packets into the transmission medium, and can formulated as
$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the data-rate of the packet and $\mathcal{\alpha}$ is the mean packet size.
Notice that taking the propagation and transmission delays into account in the formulation is straightforward, but we have avoided it for the sake of succinctness and simplicity.

@@

\text{subject to} \quad  &  P_r \leq P^{\text{max}}_{r} \quad \forall r,

@@

&p_{r,u(s,i)}^{k}  \leq P_{s}^{\text{max}}  \quad \forall i, r, s, k,\label{c12-1} \\
&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{\min} \quad \forall s, \label{c13} \\

@@

& C_r \leq C^{\text{max}}_r \quad \forall r, \label{c15}\\
&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{\text{max}}_{s} \quad \forall i, s,\label{c16} \\

@@

& 0 \leq M_s \leq M^{\text{max}}_s  \quad \forall s,\label{c16-3}\\
& \phi^{\text{\text{tot}}}  \leq \phi^{\text{max}}, \label{c19} \\

@@

Suppose, $\mathcal{R}_{{s}}^{\min}$, and $\mathcal{R}_{{s}}^{\text{max}}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.

@@

Therefore, the minimum number of PRBs that slice s with $U_s$ UEs requires is $K_s^{\min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\text{max}}}}\rceil$. 
Moreover, the maximum number of PRB that the slice s with $U_s$ UEs requires is $K_s^{\text{max}} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\min}}}\rceil$. Also, $K_s = (K_s^{\min}+K_s^{\text{max}})/2$ is the average number of required PRBs in slice s.

@@

& K_s^{\min} \leq \bar{K_s}  \leq K_s^{\text{max}}  \quad \forall s \in S_1,\label{prb1} \\

@@

\subsection{Sub-Problem 1}\label{sub1}
Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
Here, we first simplify and relax the parameters to convexify the problem.
As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{\text{max}}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
for $\rho_{u(s,i)}^{k}$.
Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.
